Constructing Biological Regulatory Networks from Process Hitting models

### 2013-07-09 parts/infer-ig.tex
proofread and check TODOs in IG and Parametrization Inference

\updated{%
The Interaction Graph (IG) is an abstract representation of the direct qualitative influences,
positives and/or negatives, between the components of the system.
As discussed in \pref{sec:intro}, the IG allows to efficiently characterise global dynamical
properties for the concrete system, such as the capability for multi-stationarity or oscillation.}

@@

\updated{%
In this section, we formally derive the IG corresponding to a given PH that is well-formed for BRN
modelling.}

%In order to infer a complete BRN, one has to find the Interaction Graph (IG) first, as some
%constraints on the parametrization rely on it.
%Inferring the IG is an abstraction step which consists in determining the global influence of
%components on each of its successors.

This section first introduces the notion of focal processes within a PH
(\pref{ssec:focal}) which is used to characterize well-formed PH for IG inference
in \pref{ssec:wf}, and as well used by the parametrization inference presented in \pref{sec:infer-K}.
Finally, the rules for inferring the interactions between components from a PH are
described in \pref{ssec:infer-IG}.
We consider hereafter a global PH $(\PHs,\PHl,\PHa)$ on which the IG inference is to be
performed.

>>>>

\updated{%
The Interaction Graph (IG) is an abstract representation of the direct qualitative influences,
positive and/or negative, between the components of the system.
As discussed in \pref{sec:intro}, the IG allows to efficiently characterise global dynamical
properties for the concrete system, such as the capability for multi-stationarity or oscillation.}

@@

\updated{%
In this section, we formally derive the IG corresponding to a given PH that is well-formed for BRN
modelling.}
%
%In order to infer a complete BRN, one has to find the Interaction Graph (IG) first, as some
%constraints on the parametrization rely on it.
%Inferring the IG is an abstraction step which consists in determining the global influence of
%components on each of its successors.
%
%
This section first introduces the notion of focal processes within a PH (\pref{ssec:focal})
which is used to characterize well-formed PH for IG inference (\pref{ssec:wf}).
%and as well used by the parametrization inference presented in \pref{sec:infer-K}.
The rules for inferring the interactions between components from a PH are
described in \pref{ssec:infer-IG}.
We consider hereafter a global PH $(\PHs,\PHl,\PHa)$ on which the IG inference is to be
performed.

### 2013-07-09 parts/infer-param.tex
proofread and check TODOs in IG and Parametrization Inference

Given the IG inferred from a PH as presented in the previous section, one can find the discrete parameters that model the behavior of the studied PH using the method presented in the following.
It relies on an exhaustive enumeration of all predecessors of each component in order to find attractor processes and returns a possibly incomplete parametrization, given the exhaustiveness of the cooperations.
The last step consists of the enumeration of all compatible complete parametrizations given this
set of inferred parameters, the PH dynamics and some biological constraints on parameters.

\subsection{Parameters inference}

>>>>

Given the IG inferred from a PH as presented in the previous section, one can find the discrete parameters
that model the behavior of the studied PH using the method presented in the following.
It relies on an exhaustive enumeration of all predecessors of each component in order to find attractor processes
and returns a possibly incomplete parametrization, given the exhaustiveness of the cooperations (\pref{ssec:infer-K}).
The last step consists of the enumeration of all compatible complete parametrizations (\pref{ssec:admissible-K}) given this
set of inferred parameters, the PH dynamics and some biological constraints on parameters.

\subsection{Parameters inference}\label{ssec:infer-K}
